Sequential rank agreement methods for comparison of ranked lists

### 2016-05-28 latex/superranker-manuscript.tex
fiddling with the corollary

Similarly we derive an upper bound for $V_L(d)$ by
\begin{align}
 V_L(d) &\leq \sup_{p \in 1,\ldots,P}\left|\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right| \int_1^P \left|\mathrm d\widehat{N}_L(p; d)\right|\label{eq:secondTerm}
\end{align}
and it follows directly from the law of large numbers that
$\widehat{A_L}(X_p) = A(X_p) + o_P(1)$ uniformly in $p$ since
$R_i(X_p)$ in equation (\ref{eq:empDistance}) for $i=1,\ldots,L$ are
independent and $Q$-identically distributed random variables with
finite second moment. Again, $\widehat{N}_L(P; d) = N(P;d) + o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}) and $N(P;d)>0$ so by the continuous mapping theorem the first factor
in equation (\ref{eq:secondTerm}) is of order $o_P(1)$ uniformly in
$p$ and $d$. The result then follows by noting that the second factor
is bounded by $P$ uniformly in $d$.
% This completes the proof.

\section{Proof of corollary \ref{cor:consistency}}

>>>>

Similarly we derive an upper bound for $V_L(d)$ by
\begin{align}
 V_L(d) &\leq \sup_{p \in 1,\ldots,P}\left|\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right| \int_1^P \left|\mathrm d\widehat{N}_L(p; d)\right|\label{eq:secondTerm}
\end{align}
and it follows directly from the law of large numbers that
$\widehat{A_L}(X_p) = A(X_p) + o_P(1)$ uniformly in $p$ since
$R_i(X_p)$ in equation (\ref{eq:empDistance}) for $i=1,\ldots,L$ are
independent and $Q$-identically distributed random variables with
finite second moment. Again, $\widehat{N}_L(P; d) = N(P;d) + o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}) and $N(P;d)>0$ so by the continuous mapping theorem the first factor
in equation (\ref{eq:secondTerm}) is of order $o_P(1)$ uniformly in
$p$ and $d$. The result then follows by noting that the second factor
is bounded by $P$ uniformly in $d$.

\section{Proof of Corollary \ref{cor:consistency}}
Let $A \triangle B = (A \setminus B) \cup (B \setminus A)$ is the symmetric difference between sets $A$ and $B$. It is then sufficient to show that
$|\widehat{\mathcal{L}}_L(\widehat{q}_L) \triangle \mathcal{L}(q)|$ converges to zero in probability as $L \rightarrow \infty$. By the triangle inequality
we have that
\begin{align}
 \left|\widehat{\mathcal{L}}_L(\widehat{q}_L) \triangle \mathcal{L}(q)\right| &= \left|\left(\widehat{\mathcal{L}}_L(\widehat{q}_L) \triangle \widehat{\mathcal{L}}_L(q)\right) \cup \left(\widehat{\mathcal{L}}_L(q) \triangle \mathcal{L}(q)\right)\right|\label{eq:corSetDiff}\\
   &\leq \left|\widehat{\mathcal{L}}_L(q) \triangle \mathcal{L}(q)\right| + \left|\widehat{\mathcal{L}}_L(\widehat{q}_L) \triangle \widehat{\mathcal{L}}_L(q)\right|\nn
\end{align}
Looking at the first term we have
\begin{align}
  \left|\widehat{\mathcal{L}}_L(q) \triangle \mathcal{L}(q)\right| &= \sum_{d=1}^P \left|1\left(\widehat{\textrm{sra}}_L(d) \geq q(d)\right)  - 1\left(\textrm{sra}(d)  \geq q(d)\right)\right|\\
   &=
\end{align}
Similarly we have
\begin{align}
\left|\widehat{\mathcal{L}}_L(\widehat{q}_L) \triangle \widehat{\mathcal{L}}_L(q)\right| &= \sum_{d=1}^P \left|1\left(\widehat{\textrm{sra}}_L(d) \geq \widehat{q}_L(d)\right) - 1\left(\widehat{\textrm{sra}}_L(d) \geq q(d)\right)\right|\\
   &=
\end{align}

%We have that 	
%\begin{align}
%  |\widehat{d^\ast_L}(\widehat{q}_L) - d^\ast(q)| &\leq  |\widehat{d^\ast_L}(q)  - d^\ast(q)| + |\widehat{d^\ast_L}(\widehat{q}_L)  - \widehat{d^\ast_L}(q_L)|
%\end{align}
%The first term is of order $o_P(1)$ by the continuous mapping theorem if a) $|\inf \widehat{\mathcal{L}}_L(q) - \inf  \mathcal{L}(q)| = o_P(1)$ and b) $|1(|\widehat{\mathcal{L}}_L(q)| = 0) - 1(|\mathcal{L}(q)| = 0)| = o_P(1)$ since $1(|\mathcal{L}(q)| > 0) = 1 - 1(|\mathcal{L}(q)| = 0)$. Similarly, the second term is of order $o_P(1)$ by the same reasoning if c) $|\inf \widehat{\mathcal{L}}_L(\widehat{q}_L) - \inf \widehat{\mathcal{L}}_L(q)| = o_P(1)$ and d) $|1(|\widehat{\mathcal{L}}_L(\widehat{q}_L)| = 0) - 1(|\widehat{\mathcal{L}}_L(q)| = 0)| = o_P(1)$.

This completes the proof.
